A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-21 main.tex
Wrote on \TConv.

% 通常のルール
The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus if you ignore stage annotations.
The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
The rule \TConst\ means any constants in the signature can appear at any stage.
For example, if we have a signature $\Sigma$ which is $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}: \textrm{bool}$,
the following derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.

@@

% \TConv
The main technical point of this paper is \TConv and type equivalence rules needed in \TConv.

>>>>

% 通常のルール
The rules \TVar , \TAbs, and \TApp\ are almost same as those in simply typed lambda calculus 
if you ignore stage annotations and kind checking.
The rule \TVar\ means that a variable can appear only at the stage in which it is declared.
It checks the type of variable $x$, $\tau$, has the proper kind for terms, $*$.
\TAbs\ also checks the kind of the type.

The rule \TConst\ means any constants in the signature can appear at any stage.
For example, if we have a signature $\Sigma$ which is $\textrm{bool} :: *, \textrm{true}: \textrm{bool}, \textrm{false}: \textrm{bool}$,
the derivation tree in Figure \ref{fig:tconst-derivation-tree} is admissible.

@@

% \TConv
The main technical point of this paper is \TConv and type equivalence rules needed in \TConv.
This rule allows ut to replace a type with another type that is equivalent.
In a type system which includes dependent types, this kind of rule is essential
because two types which have different shapes may be equivalent.
For example, when we use a matrix type which have their sizes ($\textrm{Mat}\ n\ m$),
$\textrm{Mat}\ 5\ 3$ is equivalent to $\textrm{Mat}\ (4+1)\ (1+2)$ obviously.
